\Large \includegraphics[height=\baselineskip]{title.png} \\ \vspace{0.65mm} \large \normalfont CSE 227: Computer Security - Spring 2017 \\ \textit{ University of California San Diego }

### 2017-06-12 docs/paper.tex
Review sections 1, 3, 4, 5, 6. Left: abstract, background, related work, conclusions

% Authors
\author{
{\rm Chen Lai}\\
\normalfont{\texttt{chl588@ucsd.edu}}
\and
{\rm Zhongrong Jian}\\
\normalfont{\texttt{zhjian@ucsd.edu}}
\and
{\rm J. Sidrach}\\
\normalfont{\texttt{jsidrach@ucsd.edu}}
}

@@

\section{Introduction}
Domain names were originally designed to only support ASCII characters.
Internationalized Domain Names (IDNs) were proposed back in December 1996 by Martin D\"{u}rst for the purpose of letting non-English speaking people use Internet without additional restrictions.
This extension involves representing Unicode characters in ASCII using Punycode, so that they could be then rendered back into their Unicode representation.
Homograph letters (different letters whose representation is almost, if not, the same), however, present a potential vulnerability.
For example, Cyrillic letter ``a'' can look identical to Latin letter ``a'' depending on the font.
In other languages, like Chinese, there exists many homograph letters between traditional Chinese and simplified Chinese.
Malicious attackers can then register a domain where one of the letters is actually Cyrillic but whose representation matches a Latin one.
Users could be linked to this newly registered malicious page, and they may not have any visual indication (at least without further interaction) that the page is not the one they think they are visiting.

Currently, most popular browsers will show the hostname in Unicode depends on the language setting to defend IDN attack.
For example, Google Chrome\footnote{\url{https://www.google.com/chrome}} will display IDN in Unicode only if all characters of the domain names belong to only one language and this language has to be the user's preferred language.

In this paper, we analyze the impact of this attack.
Section 2 explains past and present policies of major browsers and top level domain(TLD) registrants in an attempt to prevent the attack.
Section 3 explores relevant work in the literature related to homograph attacks.
Section 4 describes the methodology of data collection and analysis adopted in this project.
Section 5 comments the different results obtained.
Section 6 addresses the ethical concerns regarding the data collection.
Section 7 presents the conclusions obtained from this project.

@@

@@

\section{Methodology}
Our data collection involves two primary sources.
The first one is a snapshot of the \texttt{.com} and \texttt{.net} domain zone, from now on referenced as \textit{.com snapshot}.
This snapshot was provided by Verisign\footnote{\url{https://www.verisign.com/en_US/channel-resources/domain-registry-products/zone-file/index.xhtml}}, and it is dated on 2017/05/01.
It contains, mostly, the name servers of all \texttt{.com} and \texttt{.net} domains.
For the purposes of this project, only the \texttt{.com} domains were considered.

The second data source is the \textit{Alexa Top 1 million sites ranking}\footnote{\url{https://www.alexa.com/topsites}}, from now on referenced as \textit{top domains snapshot}.
It contains the most popular one million web sites, regardless whether they are \texttt{.com} domains or not.
It was also retrieved on 2017/05/01.

@@

\subsection{Data Processing}
We used the \textit{.com snapshot} to obtain all the internationalized domains of the \texttt{.com} domain zone.
All internationalized domain names are represented using Punycode, so they start with the \texttt{xn--} prefix.
Using this information we first filtered the \textit{.com snapshot} to match only the \texttt{.com} domains that start with \texttt{xn--}.
Since the \textit{.com snapshot} contains name server records, a single domain may have more than one entry in the file.
Only the domain name is relevant for this project, so the rest of the columns of the \textit{.com snapshot} were discarded.
We sorted the domains in lexicographic order, removing duplicates in the process.

We used the \textit{top domains snapshot} as a source for the canonical (non-international) domain name of a website, based on its ranking.
As we were only interested in non-internationalized domain names, so we discarded the ones that start with the prefix \texttt{xn--}.
We also removed sub-domains, as we only had top level domain names in the \textit{.com snapshot}.

\subsection{Clustering}
The underlying assumptions behind the clustering process are that homograph attacks are more likely to target popular domains, and that the million domains from the \textit{top domains snapshot} contains most of the popular domains.
To detect potential internationalized domain name homograph attacks, we cluster the internationalized domain names in the \textit{.com snapshot}.
The representative of each cluster is a homograph domain name from the \textit{top domains snapshot}.
Only clusters with more than one domain name are output.

The detection of homograph domain names is done using an algorithm to check if two strings are confusable.
This algorithm is described in the \textit{Unicode Technical Standard \#39}\footnote{\url{http://www.unicode.org/reports/tr39/#Confusable_Detection}}.
The approach followed has some caveats, that could be addressed in future work.
For instance, it does not detect a homograph of \texttt{www.google.com}, where the first ``.'' has been replaced by a similar looking Unicode character.
More sophisticated homographs can also be generated by using Unicode characters similar to ``/''.
It is also worth noting that only domain names from the \texttt{.com} zone were considered, but similar studies could be done to other top level domains following the same procedure.
All things considered, we still think this approach is a valuable first step.

@@

\subsection{Manual Classification}
The last part of the data processing was the classification of the homograph domain names.
This classification was done manually, to be able to differentiate between scam and unrelated websites.
To help with the classification and speed up the process, we queried the \textit{WHOIS} records~\footnote{\url{https://whois.icann.org}} of every homograph domain name.
Some domains expired at the time of the classification, and were subsequently deleted from the output file.

The two high level categories that were defined are \textit{Canonical} and \textit{Third Party}.
The first one, \textit{Canonical}, is employed when the domain is registered by the same organization as its canonical homograph domain name.
The second one, \textit{Third Party}, is used when the domain is registered by a different organization than its canonical homograph domain name.
Additionally, a more detailed classification was made:
\itemize{
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\item \textit{Canonical - Parking}: domain is registered but not accessible via HTTP.
\item \textit{Canonical - Redirect}: domain redirects (HTTP Status Code 301/307/308) to its canonical homograph domain name.
\item \textit{Third Party - Redirect to Canonical:} domain redirects (HTTP Status Code 301/307/308) to its canonical homograph domain name.
\item \textit{Third Party - Unrelated}: domain resolves, but the contents of the website are totally unrelated to its canonical homograph domain name.
\item \textit{Third Party - Parking}: domain is registered, but no accessible via HTTP, or when accessed, a default domain parking web page is displayed.
\item \textit{Third Party - Scam}: domain resolves, and the website displayed is a clear attempt (similar color, logos, etc.) to make users think they are visiting the canonical homograph domain name.
}

@@

We obtained 458731 domain names from the \textit{top domains snapshot} that belonged to the \texttt{.com} zone.
From the \textit{.com snapshot}, we identified a total of 1044301 internationalized domains.
However, only a low percentage of the internationalized domain names (3.68\%) had a homograph canonical domain name in the \textit{top domains snapshot}.
Even if we take into account that our homograph detection algorithm is rather limited (as described before), these results still indicate that the majority of internationalized domain names are not being used in homograph attacks.
An overview of these clustering results can be found in Table~\ref{clustering-results}.

@@

The manual classification sheds some light on how these homograph internationalized domain names are being used.
For the most part (82.34\%), the domains are registered by a third party, and not being used actively (parking).
One possible explanation for this is that the domain was bought in an attempt to be re-sold later at a higher price to the owner of the canonical homograph domain.
A detailed breakdown of this classification can be found in Table~\ref{manually-classified-idns}.

@@

\section{Ethical Considerations}
The domain information used in this project is publicly available and was voluntarily provided by the registrants of the domains.
The full \texttt{.com} domain zone snapshot won't be publicly disclosed, as its access requires a paid subscription.
The retrieval of the \textit{WHOIS} information was performed only for the homograph internationalized domain names, which were about one thousand.
It was done with a significant delay between petitions (3 seconds) in order to avoid saturating the server.

@@

TODO DELETE~\cite{ipv4sta}

>>>>

% Authors
\author{
{\rm Chen Lai\footnote{Author names are ordered lexicographically, by last name.}}\\
\normalfont{\texttt{chl588@ucsd.edu}}
\and
{\rm Zhongrong Jian\footnotemark[\value{footnote}]}\\
\normalfont{\texttt{zhjian@ucsd.edu}}
\and
{\rm J. Sidrach\footnotemark[\value{footnote}]}\\
\normalfont{\texttt{jsidrach@ucsd.edu}}
}

@@

\section{Introduction}
Domain names were originally designed to only support ASCII characters.
Internationalized Domain Names (IDNs) were proposed back in December 1996 by Martin D\"{u}rst\footnote{\url{https://tools.ietf.org/html/draft-duerst-dns-i18n-00}} for the purpose of letting non-English speaking people use Internet without additional restrictions.
This extension involves representing Unicode characters in ASCII using Punycode, so that they could be then rendered back into their Unicode representation.
Homograph letters (different letters whose representation is almost, if not, the same), however, present a potential security vulnerability.
For example, Cyrillic letter ``a'' can look identical to Latin letter ``a'' depending on the font.
In other languages, like Chinese, there exists many homograph letters between traditional Chinese and simplified Chinese.
Malicious attackers could then register a domain where one of the letters is actually Cyrillic but whose representation matched a Latin one.
Users could be linked to this newly registered malicious page, and they may not have any visual indication (at least without further interaction) that the page is not the one they think they are visiting.

In this paper, we analyze the potential impact of this type of attack, commonly refered to as IDN Homograph Attack.
Section 2 explains past and present policies of major browsers and top-level domain (TLD) registrants in an attempt to prevent the attack.
Section 3 explores relevant work in the literature related to homograph attacks.
Section 4 describes the methodology of data collection and analysis adopted in this project.
Section 5 comments the different results obtained.
Section 6 addresses the ethical concerns regarding the data collection.
Section 7 presents the conclusions obtained from this project.

@@

Currently, most popular browsers will show the hostname in Unicode depends on the language setting to defend IDN attack.
For example, Google Chrome\footnote{\url{https://www.google.com/chrome}} will display IDN in Unicode only if all characters of the domain names belong to only one language and this language has to be the user's preferred language. \ref{screenshot} show the screenshots of the original url of \url{www.google.com} and its homograph.

\begin{figure}[t]
  \includegraphics[width=\linewidth]{google.png}
  \includegraphics[width=\linewidth]{fakegoogle.png}
  \centering
  \caption{Google(top) and its homograph(bottom) on Chrome}
  \label{screenshot}
\end{figure}

@@

\section{Methodology}
Our data collection involved two primary sources.
The first one was a snapshot of the \texttt{.com} and \texttt{.net} domain zone, from now on referenced as \textit{.com snapshot}.
This snapshot was provided by Verisign\footnote{\url{https://www.verisign.com/en_US/channel-resources/domain-registry-products/zone-file/index.xhtml}}, and it is dated on 2017/05/01.
It contains, for the most part, the name servers of all \texttt{.com} and \texttt{.net} domains.
For the purposes of this project, only the \texttt{.com} domains were considered.

The second data source was the \textit{Alexa Top 1 million sites ranking}\footnote{\url{https://www.alexa.com/topsites}}, from now on referenced as \textit{top domains snapshot}.
It contains the most popular one million web sites (as ranked by Alexa), regardless whether they are \texttt{.com} domains or not.
It was also retrieved on 2017/05/01.

@@

\subsection{Data Processing}
We used the \textit{.com snapshot} to obtain all the internationalized domains of the \texttt{.com} domain zone.
All internationalized domain names are represented using Punycode, so they start with the \texttt{xn--} prefix.
Using this information we first filtered the \textit{.com snapshot} to match only the \texttt{.com} domains that start with \texttt{xn--}.
Since the \textit{.com snapshot} contains name server records, a single domain may have more than one entry in the file.
Only the domain name is relevant for this project, so the rest of the columns of the \textit{.com snapshot} were discarded.
We sorted the domains in lexicographical order, removing duplicates in the process.

We used the \textit{top domains snapshot} as a source for the canonical (non-international) domain name of a website, based on its ranking.
As we were only interested in non-internationalized domain names, we discarded the ones that start with the prefix \texttt{xn--}.
We also removed sub-domains, since we only had top-level domain names in the \textit{.com snapshot}.

\subsection{Clustering}
The underlying assumptions behind the clustering process are that homograph attacks are more likely to target popular domains, and that the million domains from the \textit{top domains snapshot} contains most of the popular domains.
To detect potential internationalized domain name homograph attacks, we clustered the internationalized domain names in the \textit{.com snapshot}.
The representative of each cluster is a homograph domain name from the \textit{top domains snapshot}, which we called canonical domain name.
Only clusters with at least one internationalized homograph domain name were output.

The detection of homograph domain names was done using an algorithm to check if two strings are confusable.
This algorithm is described in the \textit{Unicode Technical Standard \#39}\footnote{\url{http://www.unicode.org/reports/tr39/#Confusable_Detection}}.
The approach followed has some caveats, that could be addressed in future work.
For instance, it does not detect a homograph of \texttt{www.google.com}, where the first ``.'' has been replaced by a similar looking Unicode character.
More sophisticated homographs can also be generated by using Unicode characters similar to ``/''.
It is also worth noting that only domain names from the \texttt{.com} zone were considered, but similar studies could be done to other top-level domains following the same procedure.
All things considered, we still think this approach is a valuable first step.

@@

\subsection{Manual Classification}
The last part of the data processing was the classification of the homograph domain names.
This classification was done manually, to be able to differentiate between scam and unrelated websites.
To help with the classification and speed up the process, we queried the \textit{WHOIS} records\footnote{\url{https://whois.icann.org}} of every homograph domain name.
Some domains had expired at the time of the classification, and were subsequently deleted from the output file.

The two high level categories that were defined are \textit{Canonical} and \textit{Third Party}.
The first one, \textit{Canonical}, was employed when the domain is registered by the same organization as its canonical homograph domain name.
The second one, \textit{Third Party}, was used when the domain is registered by a different organization than its canonical homograph domain name.
Additionally, a more detailed classification was made:
\itemize{
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\item \textit{Canonical - Parking}: domain was registered but it was not accessible via HTTP.
\item \textit{Canonical - Redirect}: domain redirected (HTTP Status Code 301/307/308) to its canonical homograph domain name.
\item \textit{Third Party - Redirect to Canonical:} domain redirected (HTTP Status Code 301/307/308) to its canonical homograph domain name.
\item \textit{Third Party - Unrelated}: domain resolved, but the contents of the website were totally unrelated to its canonical homograph domain name.
\item \textit{Third Party - Parking}: domain was registered, but it was not accessible via HTTP, or when accessed, a default domain parking web page was displayed.
\item \textit{Third Party - Scam}: domain resolved, and the website displayed was a clear attempt (similar color, logos, etc.) to make users think they were visiting the canonical homograph domain name.
}

@@

We obtained 458731 domain names from the \textit{top domains snapshot} that belonged to the \texttt{.com} zone.
From the \textit{.com snapshot}, we identified a total of 1044301 internationalized domains.
However, only a low percentage of the internationalized domain names (3.68\%) had a matching homograph canonical domain name in the \textit{top domains snapshot}.
Even if we take into account that our homograph detection algorithm is rather limited (as described before), these results still indicate that the majority of internationalized domain names are not being used in homograph attacks.
An overview of these clustering results can be found in Table~\ref{clustering-results}.

@@

The manual classification sheds some light on how these homograph internationalized domain names are currently being used.
For the most part (82.34\%), the domains are registered by a third party, and not being used actively (parking).
One possible explanation for this is that the domain was bought in an attempt to be re-sold later at a higher price to the owner of the matching canonical homograph domain.
A detailed breakdown of this classification can be found in Table~\ref{manually-classified-idns}.

@@

\section{Ethical Considerations}
The domain information used in this project is publicly available, and was voluntarily provided by the registrants of the domains when they registered them.
The full \texttt{.com} domain zone snapshot will not be publicly disclosed, as its access requires a paid subscription.
The retrieval of the \textit{WHOIS} information was performed only for the homograph internationalized domain names, which were about one thousand.
It was performed with a significant delay between petitions (3 seconds) in order to avoid saturating the servers.

@@
